\part{What We've Learned}

{\Large ``I learned \ldots''} ~\\

	\begin{description}
		
		\item[Erich] ~\\
			\begin{itemize}
				\item  SVN: during the last week I've really gotten the hang of it
				\item  Of course, the whole planning and designing process. I did not even know there was a universally accepted designing process or diagrams.
				\item  The whole network programming portion. I had no clue about it before taking this class. Working on string passing has made me become quite comfortable with it.
				\item  The importance of javadoc. It makes code easier to understand and use, especially code that someone else has written.
				\item  Some new programs such as `Dia', `Graphviz' and others
			\end{itemize}

		\item[Matt] ~\\
			\begin{itemize}
					\item  Socket communication is not as easy as it sounds
					\item  Plan in code, not words
					\item  There are always more conditions to check
					\item  Doing everything in one method is not ideal for debugging
					\item  Communication is very critical
					\item  Code in groups (coders together in same place)
					\item  Don't ask about other people's projects
					\item  The internet is an invaluable resource for everything
					\item  When it doesn't work, rewrite it from scratch a different way
					\item  Have someone else do the whole thing
			\end{itemize}
		~\\ % may not need this, just needed to force a newline
		\item[Michael] ~\\
			\begin{itemize}
				\item Don't save ANYTHING until the last minute
				\item Set up proper group communication channels at the start of the project
					\begin{itemize}
						\item Set up the roles for group members EXPLICITLY.  Even if they change throughout, it is extrememly necessary to know who to call upon and for what.
						\item Set up certain communication rules. (ie: check your email daily, 24 hours notice for a missed meeting, contact group members before and after a missed meeting / class, etc.)
					\end{itemize}				
				\item Determine everyone's responsibilities from the start of each discrete project step.  No one should ever not know what he or she is responsible for.  The same is true for knowing what others are responsible for.
				\item A solid, collaborative approach hinges on regular, documented and transparent progress
				\item \begin{quote}`\ldots From each according to ability \ldots'\end{quote}
			\end{itemize}
		
		\item[Todd] ~\\
			\begin{itemize}
				\item Importance of javadoc and heavily commented code when working with a group so that even if you didn't write the code you can still understand what is happening.
				\item How much more complicated and complex a project becomes when you do all the paper work and planning we did.
				\item Importance of a group leader to keep everyone on track and up to date.
				\begin{itemize}
					\item (``Thank you to Mike: I feel this was your role whether you agreed to it or not'')
				\end{itemize}
				\item Putting things off until later is bad!
			\end{itemize}
			
	\end{description}